 %\documentstyle[11pt]{article}
\documentclass{article}
\usepackage{color}
\definecolor{darkblue}{rgb}{0,0,0.5}

\usepackage{hyperref}
\hypersetup{ colorlinks, urlcolor=darkblue}

%\setlength{\paperheight}{11in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{6in}
\setlength{\oddsidemargin}{-0.5in}
%\setlength{\evensidemargin}{0.5in}

%\pagenumbering{plain}

%-------------- define commands and counters ----------------------------------
\renewcommand{\baselinestretch}{1.}
\newcommand{\hs}{\hspace*}
\newcommand{\vs}{\vspace*{2mm}}
\newcommand{\dis}{\displaystyle}
\newcommand{\no}{\noindent}
\newcommand{\ns}{\vspace{6pt}\noindent}
 
%------------------------ my commands ----------------------------------------
\newcommand{\cvsectionname}[1]{\multicolumn{2}{l}{\Large \tt #1}\\\hline\\} 
\newenvironment{cvsection}[1]{\medskip \begin{tabular}{rl} \cvsectionname{#1}}{\end{tabular}}
\newcommand{\cvline}[2]{\parbox[t]{2.3cm}{\sl  \hfill #1} & \parbox[t]{14cm}{ #2 \hfill}\\\vspace{4pt}} 
\newcommand{\cvsecondaryline}[1]{ & \parbox[t]{14cm}{#1 \hfill} \\\vspace{4pt}} 
\newcommand{\cvexplanationline}[1]{ & $\triangleright$ #1 \hfill \\\vspace{4pt}} 
\newcommand{\cvtechnicalline}[2]{\parbox[t]{2.3cm}{\sl #1} & \parbox[t]{14cm}{ #2 \hfill}\\\vspace{4pt}} 
\newcommand{\cvlanguageline}[2]{\parbox[t]{2.48cm}{\sl #1} & \parbox[t]{14cm}{ #2 \hfill}\\\vspace{4pt}} 
\newcommand{\cvexperienceline}[2]{\parbox[t]{2.3cm}{\sl \hfill #1} & \parbox[t]{14cm}{{\bf #2} \hfill}\\\vspace{4pt}} 
\newcommand{\cvexperienceexplanationline}[1]{ & \parbox[t]{14cm}{$\triangleright$ #1 \hfill} \\\vspace{4pt}} 
\newcommand{\cvexperiencecontributionline}[1]{ & \parbox[t]{14cm}{\hspace{6pt} $\bullet$ #1 \hfill} \\\vspace{4pt}} 
\newcommand{\cvreferenceline}[2]{& \parbox[t]{16cm}{$\bullet$ \bf #1, \rm #2}\\\vspace{4pt}} 

\begin{document}

\pagestyle{empty}

\begin{center}
\hspace*{4.8cm}{\LARGE  \bf     Mircea Filip LUNGU}  \\[9pt]
\hspace*{4.8cm}Via Al Lido 8  \\
\hspace*{4.8cm}Lugano, Switzerland  \\
\hspace*{4.8cm}+41-078-904.3235  \\
\hspace*{4.8cm}mircea.lungu@lu.unisi.ch  \\
\hspace*{4.8cm}\href{http://www.inf.unisi.ch/phd/lungu}{http://www.inf.unisi.ch/phd/lungu}
\end{center}

\vspace{0.3cm}

\begin{cvsection}{Education}
\cvline{Oct. 2004 - ...} {PhD student in Informatics at the University of Lugano. 
% My advisor is Prof. Dr. Michele Lanza. My main research interests are in  software engineering and visualization.
}
% \cvexplanationline{Working with Prof. Dr. Michele Lanza}
% \cvexplanationline{Interested in Software Engineering, Program Comprehension, Software Visualization}

\cvline{1999 - 2004} {Student at the Faculty of Informatics from ``Politehnica'' University of Timi\c{s}oara}
% \cvexplanationline{Average grade for the 5 years: 9.6 (out of 10)}

%\cvline{1995 - 1999}{``Vasile Goldis'' High School in Arad - specialization in informatics}
%\cvexplanationline{Leaving examination mark: 9.5 (out of 10)}
\end{cvsection}



% ~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{Employment}
% ~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvexperienceline{Oct. 2004 -  ...}{Faculty of Informatics, University of Lugano, Switzerland}
\cvexperienceexplanationline{Teaching Assistant. Assisting the {\em Programming Fundamentals I} and co-teaching the {\em Software Atelier II} course. Preparing courses, grading assignments, preparing projects and exams.}

\cvexperienceline{2007, Jul-Dec}{Internship at IBM T.J. Watson Research Center}
\cvexperienceexplanationline {Co-op in the Next Generation Distributed Systems Group - implementing visualization tools for large scale distributed systems.}

\cvexperienceline{2001 - 2003}{Computervoice Systems, Romania}
\cvexperienceexplanationline{Software Developer (part-time). Working on Dependabill, a CRM system for  for the telecommunications market in the United States}
%\cvexperiencecontributionline{Team working and learning about industry demands}
%\cvexperiencecontributionline{Implementation in Visual C++}

\cvexperienceline{1999 - 2000}{Logos Highschool, Timi\c{s}oara}
\cvexperienceexplanationline{Teaching Assistant. Teaching the introductory programming course with Pascal}
%\cvexperiencecontributionline{Teaching the introductory programming course with Pascal}
\end{cvsection}



% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{Research Experience}
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvexperienceline{2005}{Consulting for a multinational software development company}
\cvexperiencecontributionline{Member of a team of specialists from across Europe}

\cvexperienceline{2004}{Diploma thesis in collaboration with Software Composition Group from University of Bern}
\cvexperiencecontributionline{Extending the Detection Strategies Mechanism}
\cvexperiencecontributionline{Developing the Magnet View visualisation tool}

\cvexperienceline{2002 - 2004}{Member of the LOOSE Research Group (LRG)}
\cvexperiencecontributionline{Focused on the evolution and re-engineering of object-oriented software systems}

\cvexperienceline{2003}{Reengineering of ProDeOOS}
\cvexperiencecontributionline{Reengineering and extending ProDeOOS - a quality assurance tool developed at LRG}
\end{cvsection}

\begin{cvsection}{Community Service}
\cvline{2005 - ...}{Organizer of the {\em PhD Talks} at the Faculty of Informatics from University of Lugano. The seminar series are the place where PhD students talk about various topics they are interested in and practice presentation skills.}
\cvline{2005 - ...}{Reviewer for the following conferences and workshops: VisSoft 2005, SoftVis 2006, CSMR 2006, MSR 2006, ICPS 2006, ASE 2006, Eurovis 2009}
\end{cvsection}




%~~~~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{Distinctions}
%~~~~~~~~~~~~~~~~~~~~~~~~
\cvline{2007}{{\em 1st Place at the ESUG Innovation Awards.} Competing with The Small Project Observatory - an online application aimed ad visualizing project portfolios. ESUG is the primary European Smalltalk Conference.}

\cvline{2006}{{\em Best poster award} for the poster entitled {\em Cutting Edge Software Visualization} presented at the 3rd International ACM Symposium on Software Visualization, Brighton, 2006}
\cvline{2003}{{\em Best software engineer} award in the contest organized by the LOOSE (The Lab on Software Engineering) at the Polytechnic University of Timisoara, Romania}
\cvline{2002}{The 2nd prize with the faculty's team at the ``Hard \& Soft'' International Contest, Suceava, Romania. The contest was based on Image Processing and the project we developed was a security sistem}
\cvline{2001}{The 3rd prize at the Mecrob programming contest, Timisoara, with the software simulation of a mechanical Robot}
\cvline{1999}{The 3rd prize at the National Contest of Educational Software, Focsani}
\cvline{1998}{The 1st prize at the Regional Computer Science Contest, Arad}
\cvline{1995 - 1999}{Other prizes at the Scholar Contests in physics, mathemathics, informatics}
\end{cvsection}



% ~~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{Publications}
% ~~~~~~~~~~~~~~~~~~~~~~
\cvline{2007} {{\bf Reverse Engineering Super-Repositories.}
Mircea Lungu, Michele Lanza, Tudor Girba, Reinout Heeck
In Proceedings of WCRE 2007 (14 Conference on Reverse Engineering), pp. 120 - 129, IEEE Computer Society, 2007.}

\cvline{} {{\bf Exploring Inter-Module Relationships in Evolving Software Systems}, Mircea Lungu, Michele Lanza. In Proceedings of CSMR 2007 (11th European Conference on Software Maintenance and Reengineering), pp. xxx - xxx, IEEE Computer Society, 2007}

\cvline{2006} {{\bf Biomedical Information Visualization}, Mircea Lungu, Kai Xu. Chapter in {\em Human Centered Visualization Environments}. Springer LNCS (to appear).}

\cvline{} {{\bf Package Patterns for Visual Archietcure Recovery}. Mircea Lungu, Michele Lanza, Tudor Girba. In Proceedings of CSMR 2006 (10th European Conference on Software Maintenance and Reengineering), pp. 183 - 192, IEEE Computer Society, 2006}

\cvline{} {{\bf Softwarenaut: Exploring Hierarchical System Decompositions} (Tool Demonstration) Mircea Lungu, Michele Lanza. In Proceedings of CSMR 2006 (10th European Conference on Software Maintenance and Reengineering), pp. 349 - 350, IEEE Computer Society, 2006}

\cvline{} { {\bf Softwarenaut: Cutting the Edge in Software Visualization}.  (Best Poster Award)
Mircea Lungu, Michele Lanza. In Proceedings of the 3rd International ACM Symposium on Software Visualization (SoftVis 2006), pp. 179-180}

\cvline{} {{\bf Mondrian: An Agile Information Visualization Framework}. Michael Meyer, Mircea Lungu and Tudor Girba. In Proceedings of the 3rd International ACM Symposium on Software Visualization, (SoftVis 2006), pp. 135-144.}
\cvline{} {{\bf The Evolution Radar: Visualizing Integrated Logical Coupling Information}.   
Marco D'Ambros, Michele Lanza, Mircea Lungu. In Proceedings of MSR 2006 (3rd International Workshop on Mining Software Repositories), pp. 26-32, 2006.}

\cvline{2005} {{\bf Interactive Exploration of Semantic Clusters}. Mircea Lungu, Adrian Kuhn, Tudor Girba, Michele Lanza. In Proceedings of VISSOFT 2005 (3rd IEEE International Workshop on Visualizing Software For Understanding and Analysis), pp. 95 - 100, IEEE CS Press, 2005. }

\cvline{2004} {{\bf Conformity Strategies: Measures of Software Design Rules }. Diploma thesis defended at the "Politehnica" University of Timisoara (Romania), Department of Computer Science }
\end{cvsection}



% ~~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{Presentations}
% ~~~~~~~~~~~~~~~~~~~~~~
\cvline{2007} {{\bf Exploring Inter-Module Relationships in Evolving Software Systems}. CSMR, Amsterdam 2007}

\cvline{2006} {{\bf A Survey of Biomedical Visualization}. HCVE, Dagstuhl 2006}
\cvline{} {{\bf Softwarenaut: Cutting Edge Software Visualization}. SoftVis, Brighton 2006}
\cvline{} {{\bf Package Patterns for Visual Architecture Recovery}. CSMR, Bari 2006}

\cvline{2005} {{\bf Interactive Exploration of Semantic Clusters}. IEEE VISSOFT, Budapest 2005}
\cvline{2003} {{\bf Optimizing Prodeoos, a tool for detecting design flaws}. SYNASC, Timisoara, 2003}
\end{cvsection}


% ~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{Selected Projects}
% ~~~~~~~~~~~~~~~~~~~~~~~~~~
\cvline{2007 - ...} {The Small Project Observatory - Portal for the visualization of the evolution of multiple projects in parallel. The project won the First Place in the ESUG Innovation Award Competiotion (ESUG - European Smalltalk Conference)}

\cvline{2006 - ...} {\href{http://www.inf.unisi.ch/phd/lungu/iretrospect/}{\bf iRetrospect}. A pet project that I started in order to be able to visualise the way I spend my time on the computer. In the same time I wanted to experience development for OS X with Cocoa and ObjectiveC.}
\cvline{2005 - ...}{\href{http://www.inf.unisi.ch/phd/lungu/softwarenaut/}{\bf Softwarenaut}. A tool for software visualization and exploration. The goal of the tool is understanding large software systems by exploring their hierarchical decompositions.  The application is developed using VisualWorks Smalltalk}
\cvline{2004}{MagnetView. A software visualization tool for visualizing software artefacts and metrics}
\cvline{2003}{Kitta. A kindergarten management application written as a team project during the LOOSE Software Engineering Laboratory. ``Best Software engineer'' award}
\cvline{2002}{Mircompilator. A compiler for a Pascal like language written in Java}
\cvline{2000}{Double-Triple-R. A 3D mechanical simulation of a robot. 3rd place at the local robotics contest}
\end{cvsection}



%\begin{cvsection}{Technical Skills}
%\cvtechnicalline{Languages:}{C/C++, Java, Smalltalk, Lisp, Prolog, Pascal,  Assembler, SQL, Php}
%\cvtechnicalline{OS:}{Windows, Unix}
%\cvtechnicalline{Tools:}{Visual Studio, Access, SQLServer, JBuilder, Delphi, Emacs, Idea, VisualWorks, Matlab}
%\cvtechnicalline{Others:}{EJB, JSP, Ant, XUnit, MySQL, MFC, Flex, Bison, DirectX, SDL}
%\end{cvsection}




\begin{cvsection}{Programming Languages} 
\cvlanguageline{Lisp} {I teach {\em Scheme} at undergraduate level and enjoy writing Lisp for small projects} %(e.g., currently I am writing a musical counterpoint generator).}

\cvlanguageline{Smalltalk} {For the last three years I have been working with {\em Smalltalk} and I came to appreciate the flexibility of the language and it's simplicity. At the university of lugano I taught smalltalk during the Programming Fundamentals course.}

\cvlanguageline{Java} {During the university years, I wrote a compiler for a simplified version of Pascal and a simplle CRM application. During my 6 months of internship at IBM I developed an Eclipse plugin for visualizing large distributed systems specifications. I supervised a bachelor project implementing a software visualization plugin for the Eclipse IDE.}

\cvlanguageline{Other} {While working as a software developer at Computervoice Systems, I acquired in-depth knowledge of  {\em Visual C++} and MFC. I have taught {\em Pascal} at highschool level. Over the years I worked with many other languages (e.g., as Assembly, Prolog, Objective C).}
\end{cvsection}



% ~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{Languages} 
% ~~~~~~~~~~~~~~~~~~~~~
\cvlanguageline{\hspace{1cm}}{{\em Romanian} is my native language. I speak fluently {\em English} and I have good knowledge of {\em Italian} and {\em French}. I have also studied {\em German} for one year during university}
\end{cvsection}
\vspace{1cm}


% ~~~~~~~~~~~~~~~~~~~~~
\begin{cvsection}{References}
% ~~~~~~~~~~~~~~~~~~~~~
\cvreferenceline{Prof. Dr. Michele Lanza}{\\Faculty of Informatics, University of Lugano. 
\\Email: michele.lanza@unisi.ch\\}
\cvreferenceline{Prof. Dr. Radu Marinescu}{\\Automation and Computer Science Faculty, ``Politehnica'' University of Timi\c{s}oara. 
\\Email: radum@cs.utt.ro\\}
\cvreferenceline{Dr. Wim de Pauw}{\\IBM T.J. Watson Research Center. 
\\Email: wim@us.ibm.ch\\}

\cvreferenceline{Dipl. Ing. Calin Sircuta}{\\Computervoice Systems, Romania. 
\\Email: sircux@computervoice.ro\\}
	
\end{cvsection}


\end{document}



