%!TEX root = resume--google.tex


\newcommand{\itu}{
	\job
		{2018 -- {\em now}}
		{Computer Science Department, IT University, Copenhagen, Denmark}
		{Associate Professor}
		{Lecturing in Software Architecture. Researching software evolution, empirical software engineering, and personalized learning.}
}
 
\newcommand{\groningen}
{
	\job
		{2015 -- 2018}
		{Johann Bernoulli Institute for Mathematics and Computer Science at the University of Groningen, Netherlands}
		{Assistant Professor}
		{Teaching Software Engineering and Introduction to Data Science. Researching software engineering and interdisciplinary projects within the DSSC Center.}
}

\newcommand{\bern}
{
	\job
		{2010 -- 2015}
		{Computer Science Institute, University of Bern, Switzerland}
		{Postdoctoral Researcher}
		{
		Researching software engineering and programming languages. Teaching Software Engineering and Compiler Construction.}
}

\newcommand{\ucirvine}
{
	\job
		{2012}
		{Department of Informatics, UC Irvine, USA}
		{Visiting Researcher}
		{Collaborative research in software evolution.}
}

\newcommand{\postlugano}
{
	\job
		{2009 -- 2010}
		{Faculty of Informatics, University of Lugano}
		{Postdoctoral Researcher}
		{Research in software evolution.}
}



\newcommand{\ibm}{

	\job 
	% {Jul -- Dec, 2007}
	{2007}
	{IBM TJ Watson Research Center, NY, USA}
	{Visiting Researcher}
	{Visualizing distributed systems with Wim De Pauw and Anand Ranganathan.}

}
	% \job 
	% {2004 -- 2009}
	% {Faculty of Informatics, University of Lugano}
	% {PhD Student}
	% {Conducting research in software evolution, visualization, and large scale software analysis}


	% \job
	% {2001 -- 2003}
	% {Computervoice Systems, Timisoara, RO}
	% {Software Engineer}
	% {Writing customer management software for several telecommunication companies from the US}

	% \job
	% {1999 -- 2001}
	% {Logos Professional Highschool, Timisoara, RO}
	% {Instructor}
	% {Teaching Introduction to Programming with Pascal}



