
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ==========================================================
\begin{enumerate}
\item Amir Aryani, Fabrizio Perin, Mircea Lungu, Abdun Naser Mahmood, and Oscar Nierstrasz. \emph{Predicting dependences using domain-based coupling}. In Journal of Software: Evolution and Process 26(1), pp. 50-76, 2014. 

\item Mircea Lungu, Michele Lanza, and Oscar Nierstrasz. \emph{Evolutionary and Collaborative Software Architecture Recovery with Softwarenaut.}  In Science of Computer Programming 79(0) p. 204 - 223, 2014.

\item Lile Hattori, Marco D'Ambros, Michele Lanza, and Mircea Lungu. \emph{Answering software evolution questions: An empirical evaluation}. In Information and Software Technology 55(4) p. 755 - 775, January 2013

\item Erwann Wernli, Mircea Lungu, and Oscar Nierstrasz. \emph{Incremental Dynamic Updates with First-class Contexts}. In Journal of Object Technology 12(3) p. 1:1-27, August 2013.

\item Niko Schwarz, Mircea Lungu, and Oscar Nierstrasz. \emph{Seuss: Decoupling responsibilities from static methods for fine-grained configurability}. In Journal of Object Technology 11(1), 2012.

\item Lile Hattori, Alberto Bacchelli, Michele Lanza, and Mircea Lungu. \emph{Erase and rewind: Learning by replaying examples.} In Software Engineering Education and Training, Conference on p. 558, 2011.

\item Marco D'Ambros, Michele Lanza, Mircea Lungu, and Romain Robbes. \emph{On Porting Software Visualization Tools to the Web}. In In Journal on Software Tools for Technology Transfer 13 pp. 181 -- 200, 2011.

\item Mircea Lungu, Michele Lanza, Tudor G\^irba, and Romain Robbes. \emph{The Small Project Observatory: Visualizing Software Ecosystems.} In Science of Computer Programming, Elsevier 75(4) p. 264-275, April 2010.

\item Marco D'Ambros, Michele Lanza, and Mircea Lungu. \emph{Visualizing Co-Change Information with the Evolution Radar.} In Transactions on Software Engineering (TSE) 35(5) p. 720 - 735, 2009.
\end{enumerate}




