%!TEX root=CV_Publist_MirceaLungu.tex
\begin{enumerate}

\item Niko Schwarz, Mircea Lungu, and Romain Robbes. On how often code is cloned across repositories. In Proceedings of the 2012 International Conference on Software Engineering, ICSE 2012 p. 1289--1292, IEEE Press, Piscataway, NJ, USA, 2012


\item Romain Robbes, Mircea Lungu, and David Roetlisberger. \emph{How Do Developers React to API Deprecation? The Case of a Smalltalk Ecosystem.} In Proceedings of the 20th International Symposium on the Foundations of Software Engineering (FSE'12), p. 56:1 - 56:11, 2012.

\item Niko Schwarz, Mircea Lungu, and Romain Robbes. \emph{On How Often is Code Cloned Across Repositories.} In Proceedings of ICSE 2012 p. 1289--1292, IEEE Press, Piscataway, NJ, USA, 2012.

\item Erwann Wernli, Mircea Lungu, and Oscar Nierstrasz. \emph{Incremental Dynamic Updates with First-class Contexts.} In Objects, Components, Models and Patterns, Proceedings of TOOLS Europe 2012, p. 304-319, 2012.


\item Amir Aryani, Fabrizio Perin, Mircea Lungu, Abdun Naser Mahmood, and Oscar Nierstrasz. \emph{Can We Predict Dependencies Using Domain information?.} In Proceedings of the 18th Working Conference on Reverse Engineering (WCRE 2011), October 2011. 

\item Lile Hattori and Alberto Bacchelli and Michele Lanza and Mircea Lungu. \emph{Erase and rewind  --  Learning by replaying examples}. In Proceedings of the 24th Conference on Software Engineering Education and Training (CSEET), 2011, Hawaii. 

\item Lile Hattori, Marco D'Ambros, Michele Lanza, and Mircea Lungu. \emph{Software Evolution Comprehension: Replay to the Rescue.} In Proceedings of the 19th International Conference on Program Comprehension, p. 161-170, IEEE Computer Society Press, 2011. 
\item 
%\fbox{$\star$}
Romain Robbes and Mircea Lungu. \emph{A Study of Ripple Effects in Software Ecosystems (NIER).} In Proceedings of the 33rd International Conference on Software Engineering (ICSE 2011), p. 904-907, May 2011. 

\item Niko Schwarz, Mircea Lungu, and Oscar Nierstrasz. \emph{Seuss: Cleaning up Class Responsibilities with Language-based Dependency Injection.} In Objects, Components, Models and Patterns, Proceedings of TOOLS Europe 2011, LNCS 33 p. 276-289, Springer-Verlag, 2011. 

\item Toon Verwaest, Camillo Bruni, Mircea Lungu, and Oscar Nierstrasz. \emph{Flexible object layouts: enabling lightweight language extensions by intercepting slot access.} In Proceedings of the 2011 ACM international conference on Object oriented programming systems languages and applications, OOPSLA '11 p. 959-972, ACM, New York, NY, USA, 2011. 
\item 
%\fbox{$\star$}
Mircea Lungu, Romain Robbes, and Michele Lanza. \emph{Recovering Inter-Project Dependencies in Software Ecosystems.} In ASE'10: Proceedings of the 25th IEEE/ACM International Conference on Automated Software Engineering, ACM Press, 2010. 
\item Marco D'Ambros, Mircea Lungu, Michele Lanza, and Romain Robbes. \emph{Promises and Perils of Porting Software Visualization Tools to the Web.} In Proceedings of WSE 2009 (11th IEEE International Symposium on Web Systems Evolution), p. 109-118, IEEE CS Press, 2009.
\item 
%\fbox{$\star$}
Mircea Lungu and Michele Lanza. \emph{Exploring Inter-Module Relationships in Evolving Software Systems.} In Proceedings of CSMR 2007 (11th European Conference on Software Maintenance and Reengineering), p. 91-100, IEEE Computer Society Press, Los Alamitos CA, 2007.
\item 
%\fbox{$\star$}
Mircea Lungu, Michele Lanza, Tudor G\^irba, and Reinout Heeck. \emph{Reverse Engineering Super-Repositories.} In Proceedings of WCRE 2007 (14th Working Conference on Reverse Engineering), p. 120-129, IEEE Computer Society Press, Los Alamitos CA, 2007. 
\item Romain Robbes, Michele Lanza, and Mircea Lungu. \emph{An Approach to Software Evolution Based on Semantic Change.} In Proceedings of FASE 2007 (10th International Conference on Fundamental Approaches to Software Engineering), p. 27-41, 2007.

%\item Marco D'Ambros, Michele Lanza, and Mircea Lungu. \emph{The Evolution Radar: Integrating Fine-grained and Coarse-grained Logical Coupling Information.} In Proceedings of MSR 2006 (3rd International Workshop on Mining Software Repositories), p. 26 - 32, 2006.
%\item Mircea Lungu, Michele Lanza, and Tudor G\^irba. \emph{Package Patterns for Visual Architecture Recovery.} In Proceedings of CSMR 2006 (10th European Conference on Software Maintenance and Reengineering), p. 185-196, IEEE Computer Society Press, Los Alamitos CA, 2006. 
%\item Michael Meyer, Tudor G\^irba, and Mircea Lungu. \emph{Mondrian: An Agile Visualization Framework.} In ACM Symposium on Software Visualization (SoftVis'06), p. 135-144, ACM Press, New York, NY, USA, 2006. 


\end{enumerate}